---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Semi-Distance Correlation and MV Index: Measure Dependence Between Categorical and Continuous Variables
<!-- badges: start -->
[![R-CMD-check](https://github.com/wzhong41/semidist/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/wzhong41/semidist/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
The goal of package `semidist` is to provide an easy way to implement the 
semi-distance methods (Zhong et al., 2023) and MV index methods 
(Cui, Li and Zhong, 2015; Cui and Zhong, 2019).

## Installation
To install `semidist`, 
``` r
install.packages("semidist")
```

## Example
Here is a simple example showing how to use `semidist` to measure the dependence
between a categorical variable and a multivariate continuous variable, and apply
the measure on testing the independence and conduct groupwise feature screening.

```{r example}
library(semidist)
X <- mtcars[, c("mpg", "disp", "drat", "wt")]
y <- factor(mtcars[, "am"])

sdcov(X, y)
sdcor(X, y)

sd_test(X, y)

sd_sis(X, y, d = 2)

# Suppose we have prior information for the group structure as
# ("mpg", "drat"), ("disp", "hp") and ("wt", "qsec")
group_info <- list(
  mpg_drat = c("mpg", "drat"),
  disp_wt = c("disp", "wt")
)
sd_sis(X, y, group_info, d = 2)

```


## References
1. Wei Zhong, Zhuoxi Li, Wenwen Guo and Hengjian Cui. (2023) “Semi-Distance Correlation and Its Applications.” *Journal of the American Statistical Association.*
1. Hengjian Cui and Wei Zhong (2019). “A Distribution-Free Test of Independence
Based on Mean Variance Index.” *Computational Statistics & Data Analysis*, 139,
117-133.
1. Hengjian Cui, Runze Li and Wei Zhong (2015). “Model-Free Feature Screening
for Ultrahigh Dimensional Discriminant Analysis.” *Journal of the American
Statistical Association*, 110, 630-641.
